Quality Assesment of OpenStreetMap Footpath Data

### 2020-06-15 report/report.tex
Reduced first paragraph in the abstract
More technically oriented abstract

\begin{abstract}
Modeling cities in 3D has long been a topic of interest in field of computer graphics.
It is often desirable to recreate real-world cities in 3D applications such as urban design software and video games, and the topic of 3D city reproduction comes with its own set of unique challenges, at the base of which lies procedual rendering of 3D road networks.
So far there have been a lot of research in modelling of road networks, but these projects have often focused on the road networks designated for cars and public transit, and seldom on pedestrian footpaths.

This project assesses the feasibility of reconstructing a city from OpenStreetMap (OSM) road and building data, and will focus on the feasibility of including pedestrian footpaths, by examining how common it is that these footpaths collide with other map features.
In the collision detection process, the margin of error has been taken as the positional error in the OSM dataset, which has been obtained by comparing OSM data to the Swedish University of Agricultural Sciences (SLU) building datset with known accuracy.

It was found that footpaths were less problematic than other road types (primary, secondary, residential), in terms of feature collisions, and thus should pose no more problems in 3D city reproduction than other road types.
The report concludes with a study of the remaining challenges in 3D city reproduction.

@@

% NOW-NOW:
% TODO: Make clear that a footpath is a type of road. Even sidewalks that run along main roads are classified as roads in OSM.
% TODO: Abstract: Reduce first paragraph (background)
% TODO: Use overlap instead of collision outside of technical contexts

% NOW:
% TODO: Introduce concepts: Collision, overlap, error
% TODO: Come up with a sentence that explains why errors could cause overlap. Repeat it in Introduction, research question and the abstract
% TODO: The word footpath does not appear anywhere in the TOC
% TODO: Abstract: Provide more detail about what was done and how it was evaluated - rephrase "In the collision detection process"

>>>>

\begin{abstract}
Modeling cities in 3D has long been a topic of interest in field of computer graphics.
It is often desirable to recreate real-world cities in 3D applications such as urban design software and video games, and the topic of 3D city reproduction comes with its own set of unique challenges, at the base of which lies procedual rendering of 3D road networks.

This project assesses the feasibility of reconstructing a city from OpenStreetMap (OSM) road and building data, and will focus on the feasibility of including pedestrian footpaths, by examining how common it is that these footpaths collide with other map features.
To examine this, a slice of the OSM dataset in the Stockholm area has been taken, and each road has been assigned with standard withds according to swedish regulation, after which a geometrical algorithm was applied to all road pairs to obtain the average amount of road overlap.
It was found that footpaths were less problematic than other road types (primary, secondary, residential), in terms of feature collisions, and thus should pose no more problems in 3D city reproduction than other road types.

As a part of this study, the positional accuracy of the OSM dataset was calculated by comparing points of OSM building footprints to those in the Swedish University of Agricultural Sciences (SLU) building datset, whose accuracy is known. The positional accuracy determines the maximum tolerance in distance between points before it is certain that a road overlaps with another road or building.

@@

% NOW-NOW:
% TODO: Make clear that a footpath is a type of road. Even sidewalks that run along main roads are classified as roads in OSM.
% TODO: Use overlap instead of collision outside of technical contexts

% NOW:
% TODO: Introduce concepts: Collision, overlap, error
% TODO: Come up with a sentence that explains why errors could cause overlap. Repeat it in Introduction, research question and the abstract
% TODO: The word footpath does not appear anywhere in the TOC
